Modeling Outbreak Frequency by Season and Pathogen: Insights and Predictions for 2025

### 2024-12-04 paper/paper.qmd
Modify the reference and the package using text

Our analysis was conducted using the statistical programming language R [@citeR], leveraging a suite of packages to facilitate efficient data manipulation, modeling, and visualization. Data cleaning, transformation, and visualization were handled using `tidyverse` [@tidyverse] and `dplyr` [@dplyr]. The core analysis used Poisson regression models to explore relationships between outbreak counts and key variables, including pathogen type, seasonal variation, and outbreak settings. These models were implemented using the flexible framework offered by `rstanarm` [@rstanarm] for model development and extensions. Efficient data integration was achieved through `arrow` [@arrow], and modeling workflows were supported using `modelr` [@modelr] within the tidyverse framework. Model summaries were generated using `modelsummary` [@modelsummary], while `ggplot2` [@ggplot2] was employed for creating visualizations. Enhanced table outputs were produced with `kableExtra` [@kableExtra], and dynamic report generation was performed with `knitr` [@citeknitr]. File management, including reading parquet files, was streamlined with `here` [@citehere].

>>>>

Our analysis was conducted using `R` [@citeR], leveraging packages for efficient data manipulation, modeling, and visualization. Data cleaning, transformation, and visualization were facilitated by `tidyverse` [@tidyverse] and `dplyr` [@dplyr]. Poisson regression models were implemented with `rstanarm` [@rstanarm] for flexible modeling and extensions. Data integration was achieved with `arrow` [@arrow], while modeling workflows were supported using `modelr` [@modelr]. Summaries were generated with `modelsummary` [@modelsummary], and visualizations were created using `ggplot2` [@ggplot2]. Enhanced table outputs were produced with `kableExtra` [@kableExtra], dynamic reporting was handled by `knitr` [@citeknitr], file management was streamlined with `here` [@citehere], and Model API deployment was performed with `plumber` [@citeplumber].
